Online learning methods for financial time series forecasting

### 2017-11-20 slides/defense-slides.tex
adding Online Learning slide

\begin{frame}
\frametitle{Motivation}
Most financial time series are non-stationary in nature. This implies that the statistical properties, such as mean and variance of the data change over time. Therefore, financial time series forecasting is still a challenge.
\begin{figure}
\includegraphics[width=0.4\paperwidth]{img/forecast}
\end{figure}

@@

@@

@@

%\frametitle{$\Omega$ matrix properties}
%The matrix $\Omega$ has the following properties:
%\item If $\Omega = 0$ there is no cointegration
%\item If $rank(\Omega)=l$ i.e full rank, then the time series are not
%I(1) but stationary
%\item If $rank(\Omega)=r,\quad 0 < r < l$ then, there is cointegration
%and the matrix $\Omega$ can be expressed as $\Omega =
%\alpha \beta^\top$, where $\alpha$ and $\beta$ are $(l \times r)$
%matrices and $rank(\alpha)=rank(\beta)=r$.
%The columns of $\beta$ contains the cointegration vectors and the rows of
%$\alpha$ correspond with the adjusted vectors. $\beta$ is obtained by Johansen
%procedure whereas $\alpha$ has to be determined as a
%variable in the VECM.

>>>>

\begin{frame}
\frametitle{Motivation}
Most financial time series are non-stationary in nature. This implies that the statistical properties, such as mean and variance of the data change over time. Therefore, financial time series forecasting is still a challenge.
\begin{figure}
\includegraphics[width=0.4\paperwidth]{img/forecast}
\end{figure}
\end{frame}

@@

\begin{frame}
\frametitle{$\Omega$ matrix properties}
The matrix $\Omega$ has the following properties:
\begin{itemize}
\item If $\Omega = 0$ there is no cointegration
\item If $rank(\Omega)=l$ i.e full rank, then the time series are not
I(1) but stationary
\item If $rank(\Omega)=r,\quad 0 < r < l$ then, there is cointegration
and the matrix $\Omega$ can be expressed as $\Omega =
\alpha \beta^\top$, where $\alpha$ and $\beta$ are $(l \times r)$
matrices and $rank(\alpha)=rank(\beta)=r$.
\end{itemize}
The columns of $\beta$ contains the cointegration vectors and the rows of
$\alpha$ correspond with the adjusted vectors. $\beta$ is obtained by Johansen
procedure whereas $\alpha$ has to be determined as a
variable in the VECM.
\end{frame}

@@

\begin{frame}
\frametitle{Online learning}
\begin{figure}
\includegraphics[width=0.8\paperwidth]{img/onlinelearning}
\end{figure}
\end{frame}

@@
